literate statistic programming
=========================================

## 一、提到r代码的可读性  
1. indenting：缩进，设置成8  
2. 右边距，设置成80  


## 二、markdown文件可以很容易地转换成HTML文件，语法很简单  
1. *italics 斜体*    
2. 标题 heading  
    #main heading  
    ##secondary heading  
    ###tertiary heading  
3. unordered list  
 * apple  
 * banana  
 * pear

4. ordered list  
 1. monday  
 2. thuesday  
 3. wednesday  
5. links  
第一种方式：链接指向的地址写在（）里，链接文字写在【】里，到时链接会蓝色下划线。  
    [John Hopkin Bloomberg School of Public Health](http://www.jhsph.edu/)  
    [Download R](http://www.r-project.org/)  
    [RStudio](http://www.rstudio.com/)  
第二种方式： 链接地址写在文章最下方，链接文字写在【】里，后面跟一个链接地址的引用。  
    I spend so much time reading [R blogger][1] and [Simply Statistics][2]!  

6. new lines:在行末加上a double space  

## 三、R markdown，把r代码嵌入到markdown文件中，代码执行的结果也会自动添加到markdown文件中
1. knitr package：convert R markdown to standard markdown
2. markdown package: convert markdown to html
3. when you use knitr in RStudio,you write the RMarkdown（.Rmd) and knitr produce a markdown file (.md),and it convert markdown file into html by default.You should not edit the .md or .html file until you are finished.  
4. slidify package: used to create slides
5. r code chunks    
```{r firstchunk}
summary(cars$dist)
plot(cars)
```  
 * you can name a code chunck
 * use "echo=FALSE" in {} after code chunck name(if any),in order to not echo the code in the result .html,but just show the result of the code.
```{r secondchunk,echo=FALSE}  
  summary(cars$dist) 
```  
 * use "results=hide" to hide the result of the code chunk,just show the code chunk itself.
```{r thirdchunk,results="hide"}
  summary(cars$dist)
``` 
  * use "result=asis" to print the result verbatim.compare with the firstchunk.
```{r thirdchunk1,results="asis"}
  summary(cars$dist)
``` 

 * inline text computations  
```{r fourthchunk}
time <- format(Sys.time(),"%a %b %d %X %Y")  
rand <- rnorm(1)  
```
the current time is `r time`. the random number produced is `r rand`.  

  * use fig.height=numeric and fig.width to adjust figure size
let's first simulate some data
```{r}  
x <- rnorm(100);
y <- x + rnorm(100,sd=0.5)
```
Here is a scatterplot of the data,use fig.height=4 to adjust figure
```{r fifthchunk,fig.height=4}
par(mar=c(5,4,1,1),las=1)
plot(x,y,main="My Simulated Data")
```  
  * making tables with xtable  
```{r sixthchunk}
library(datasets)
data(airquality)
fit <- lm(Ozone ~ Wind + Temp + Solar.R,data=airquality)
summary(fit)
```
Here is a table of regression coefficients
```{r seventhchunk,results='asis'}
library(xtable)
xt <-xtable(summary(fit))
print(xt,type="html")
```  
  * setting global options
  write opts_chunk$set(echo=FALSE,results="hide") in a code chunk, and it will apply to all the chunks.A chunk with its own options will override the default global options.

  * use cache=TRUE option to cache (store) results of computation,after the first run,results are loaded from cache.
    * This option is set on a chunk-by-chunk basis.  
    * If the data or code (or anything external) changes, you need to re-run the cached code chunks.  
    * chunks with significat side effects may not be cacheable  
6. knit2html("document.Rmd")  
  browseURL("document.html")  
  





=============================================
用第二种方式做link的链接地址一定要写在文章末，写在文件中间不生效
[1]:http://www.r-bloggers.com/ "R blogger"  
[2]:http://simplystatics.org/ "Simply Statistics"  
